Statistical Geometry of the turbulent ISM - I. Field lines

### 2015-01-11 field_lines/paper.tex
Added some refernces and tidied

\section{Introduction}
%FAG rephrase
%The results presented in this paper are based on simulations of the multiphase interstellar medium (ISM) by Gent \textsl{et al} in \citep{GSFSM13} and \citep{GSSFM13}, %further referencing to Paper I & II needed here.
The results presented in this paper are based on simulations of the multiphase 
interstellar medium (ISM) reported in \citet{GSFSM13} and \citet{GSSFM13}, %further referencing to Paper I & II needed here.
subsequently referred to as \HD\, and \MHD, respectively.
%end FAG
%FAG rephrase
In particular we consider a model, identified as B1$\Omega$s in \MHD.
Supernova(SN)-driven turbulence is applied to ISM in a section of a spiral
galaxy differentially rotating, stratified about the galactic disk and subject
to, radiative cooling, photoelectric heating and other transport processes.
The rate and distribution of SN explosions, gravity and angular momentum are 
consistent with observational parameters for the solar neighbourhood.
A nano Gauss seed magnetic field is applied and amplified by dynamo until it
saturates with a mean magnetic stength of a few micro Gauss, remarkably 
consistent with observed estimates for the Milky Way.

@@

\section{The mean magnetic field}
When considering the mean-field decomposition of the magnetic field, the notation used by \citep{GSSFM13} is adopted.

>>>>

\section{Introduction}
FAG -- notes -- include Beck, Fletcher, Berkhuijsen observations of magnetic 
fields \citep{2013AN....334..548B, MNR18065} and observation/estimates of multiphase structure \citep{dummy}
\citep{CS74,M077}

%FAG rephrase
%The results presented in this paper are based on simulations of the multiphase interstellar medium (ISM) by Gent \textsl{et al} in \citep{GSFSM13} and \citep{GSSFM13}, %further referencing to Paper I & II needed here.
The results presented in this paper are based on simulations of the multiphase 
interstellar medium (ISM) reported in \citet{GSFSM13} and \citet{GSSFM13}, %further referencing to Paper I & II needed here.
subsequently referred to as \HD\, and \MHD, respectively.
%end FAG
%FAG rephrase
In particular we consider a model, identified as B1$\Omega$s in \MHD.
Supernova(SN)-driven turbulence is applied to ISM in a section of a spiral
galaxy differentially rotating, stratified about the galactic disk and subject
to, radiative cooling \citep{Sarazin87,Wolfire95}, photoelectric heating
\citep{Wolfire95} and other transport processes.
The rate and distribution of SN explosions, gravity \citep{Kuijken89} and 
angular momentum are consistent with observational parameters for the solar
neighbourhood \citep{F01}.
A nano Gauss seed magnetic field is applied and amplified by dynamo until it
saturates with a mean magnetic stength of a few micro Gauss, remarkably 
consistent with observed estimates for the Milky Way \citep{dummy}.

@@

%-----------------------------------------------------------------------------
\section{The mean magnetic field}
%-----------------------------------------------------------------------------
\section{The mean magnetic field}

%FAG rephrase
The decomposition of the magnetic field into mean and fluctuating (random) 
field follows \MHD.
%When considering the mean-field decomposition of the magnetic field, the notation used by \citep{GSSFM13} is adopted.
